Evaluating a simplified forecast model in comparison to the European forecasting hub ensemble

### 2022-09-23 paper/paper.Rmd
add references for emulation

Here, we focus on addressing the issues of resource cost, and interpretability.
In climate forecasting, emulation approaches have been used to circumvent some of the resource requirement issues by training a simplified model, usually, a non-parametric statistical model, to replicate the behaviour of either the entire model or sub-components [@REF].
However, within epidemiological modelling, we often want to use our models for applications other than forecasting (such as learning about underlying disease dynamics or developing scenarios) and have fewer insights beyond forecast performance on which to base our mechanistic assumptions.
This means that non-parametric emulation is less suitable for use in epidemiological forecasting (while noting that epidemiological scenario analysis in-sample emulation using non-parametric methods may have a role [@REFLSHTMTBEMULATOR]).

>>>>

Here, we focus on addressing the issues of resource cost, and interpretability.
In climate forecasting [@Castelletti2012-bs; @Edwards2021-lv; @Williamson2013-qx], as well as in other fields such as astrophysic [@Vernon2014-ov], emulation approaches have been used to circumvent some of the resource requirement issues by training a simplified model, usually, a non-parametric statistical model, to replicate the behaviour of either the entire model or sub-components [@REF].
However, within epidemiological modelling, we often want to use our models for applications other than forecasting (such as learning about underlying disease dynamics or developing scenarios) and have fewer insights beyond forecast performance on which to base our mechanistic assumptions.
This means that non-parametric emulation is less suitable for use in epidemiological forecasting (while noting that epidemiological scenario analysis in-sample emulation using non-parametric methods may have a role [@Iskauskas2022-fz]).
